---
output:
  bookdown::word_document2:
    reference_docx: "template.docx"
title: "Trends in smooth cordgress biomass in the Virginia Coast Reserve"
bibliography: testbib.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(mgcv)
library(gratia)
library(ggeffects)

load(here::here("data/model_fitting_results.rdata"))
load(here::here("data/processed_spartina_biomass.rdata"))
```

# Introduction
## Introduction
### Introduction
#### Introduction

**bold**  
*italics*  
this is a <sup>superscript</sup>  
this is a <sub>subscripts</sub>  

# Methods

We can easily write pretty mathematical formulas. For example, a simple linear model is given by

$$y_i = \beta x_i + \epsilon_i\;\;\;\;\textrm{where}\;N\sim(0, \sigma^2)$$
$y_i$ is the response variable.

The model formula for the GAM was 

````
mean_transect_biomass ~ s(year) +
                        s(year, habitat_type, bs = "fs") +
                        s(year, site, bs = "fs")
````

Here's a random number: `r round(rnorm(1), 2)`

# Results

```{r}
mod_summ <- summary(mod)
dev_expl <- mod_summ$dev.expl
trend_pval <- mod_summ$s.table[10]
```

Results from the GAM showed that there was a significant non-linear trend in *S. alterniflora* biomass density through time (P = `r round(trend_pval, 2)`).

```{r trend-plt, fig.cap = "*S. alterniflora* trends in the VCR.", fig.width = 6,fig.height = 3.5}
vcr_pred_plt
```

We used the GAMM formulation from @pedersen2019.

We found a trend blah blah (Fig. \@ref(fig:trend-plt)).

