---
title: "Trends in smooth cordgrass biomass in the Virginia Coast Reserve"
description: |
  A new article created using the Distill format.
author:
  - name: Sean Hardison
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,dpi=300,fig.width=5,warning = F, message = F,echo = F)
library(tidyverse)
library(mgcv)
library(gratia)

#load data
load(here::here("data/model_fitting_results.rdata"))
load(here::here("data/processed_spartina_biomass.rdata"))
```

# Introduction
## Introduction
### Introduction
#### Introduction

**bold**
*italics*
this is a <sup>superscript</sup> using HTML tag
this is a <sub>subscript</sub> using an HTML tag

# Methods

We can easily write pretty mathematical formulas. For example, a simple linear model is given by 

$$y_i = \beta x_i + \epsilon_i\;\;\;\;\textrm{where}\;\epsilon_i\sim N(0,\sigma^2)$$
To write equations inline, you use a single \$ rather than 2. This model says that $y_i$ is the covariate $x_i$ multiplied by the constant $\beta$ plus a random term $\epsilon_i$.

Alternatively, you can report your model as it was formulated as code using backticks (four backticks for reporting blocks of code):

````
mean_transect_biomass ~ s(year) +
                        s(year, habitat_type, bs = "fs") + 
                        s(year, site, bs = "fs")
````

Or you can include code in-line with a single `backtick`.

Code can even be evaluated in-line. For example, here's a random number: `r round(rnorm(1),2)`.

# Results

```{r}
mod_summ <- summary(mod)
dev_expl <- mod_summ$dev.expl
trend_pval <- round(mod_summ$s.table[10], 1)
```

Results from the GAM showed that there was a significant non-linear trend in *S. alterniflora* biomass density over time across sites and habitats (P = `r trend_pval`). The model explained `r round(dev_expl, 2)`% of deviance. 

```{r}
# figures!

```

# figures
    * width, height, dpi
    * patchwork
    * .png
# citations (.bib files)
# putting it all together (sourcing scripts in .rmds)
# word documents
    * .csl files (citation style language)
    * template files
    * cover pages
    
    
    


